% This is the translated version of the Introduction chapter for 「上田次郎のなぜベストを尽くさないのか？」
% ISBN:978-4-05-402528-8
% Date of publishing: July 2004
% Number of pages: ~192
% Translation by Jamie Taylor (seppydude@gmail.com) 2012

% The following is a last of escape sequences that can be used to create latin characters with accents and such
%\`{o}	ò	grave accent
%\'{o}	ó	acute accent
%\^{o}	ô	circumflex
%\"{o}	ö	umlaut or dieresis
%\H{o}	ő	long Hungarian umlaut (double acute)
%\~{o}	õ	tilde
%\c{c}	ç	cedilla
%\k{a}	ą	ogonek
%\l		ł	l with stroke
%\={o}	ō	macron accent (a bar over the letter)
%\b{o}	o	bar under the letter
%\.{o}	ȯ	dot over the letter
%\d{u}	ụ	dot under the letter
%\r{a}	å	ring over the letter (for å there is also the special command \aa)
%\u{o}	ŏ	breve over the letter
%\v{s}	š	caron/hacek ("v") over the letter
%\t{oo}	o͡o	"tie" (inverted u) over the two letters

% Ensure that the footnote count is reset for each chapter
\setcounter{footnote}{0}
\setcounter{endnote}{0}

\chapter*{A Note From The Translator}

\epigraph{``I gotta take notes when things occur to me"}{--- \textup{Jeff Bridges}, Unknown}

\section*{Reasons for Translating This Book}

Throughout the TRICK series (including the TV Show, the Specials and the Films), Ueda Jiro - the male lead - constantly refers to books that he has written. These books are based on his experiences solving paranormal crimes. These crimes are solved by Yamada Naoko - the female lead - working alongside Ueda. The books (``Why don't you do your best?''\endnote{(日本科学技術大学教授上田次郎のなぜベストを尽くさないのか?} (known as ``Naze Besto''), `Come over, Spiritual Phenomena''\endnote{日本科学技術大学教授上田次郎のどんと来い、超常現象 (単行本)} (known as ``Donto Koi'') , etc.) are used by supporting characters to point out how brave and smart Ueda is. The joke being that Ueda isn't, really, either. He's a physics professor at \ruby{東}{とう}\ruby{大}{だい}\endnote{\ruby{東}{とう}\ruby{京}{きょう}\ruby{大}{だい}\ruby{学}{がく} is often abbreviated to T\^{o} Dai}, but he often confuses basic magic tricks for paranormal phenomena. He is also very easily scared out of his wits.

\par When I found out that the books referenced in the show had been published, as a series of self-help style books, I decided that I would need to read them, as they would provide more insight into the characters. A cursory web-search showed me that none of the books had been translated, so I decided to order a copy of one of the books. I chose ``Naze Besto'' because it seemed to be used for more jokes in the series than ``Donto Koi''.


\section*{Who Are All These People?}

Trick is a Japanese comedy starring \ruby{阿}{あ}\ruby{部}{べ}\ruby{寛}{ひろし}\endnote{Abe Hiroshi} and \ruby{仲}{なか}\ruby{間}{ま}\ruby{由}{ゆ}\ruby{紀}{き}\ruby{恵}{え}\endnote{Nakama Yukie} as \ruby{上}{うえ}\ruby{田}{だ}\ruby{次}{じ}\ruby{郎}{ろう}\endnote{Ueda Jiro} and \ruby{山}{やま}\ruby{田}{だ}\ruby{奈}{な}\ruby{緒}{お}\ruby{子}{こ}\endnote{Yamada Naoko}, respectively.

\par 上田 is a professor of Physics at Tokyo University and uses logic and physics as a basis for his understand of the world and the people within it. Whereas 奈緒子 is a down on her luck, and (usually) out of work magician, who uses intuition and her magical training to see through most illusions.

\par 上田 is contacted by people to help them to understand or debunk paranormal phenomena (for instance: curses, good luck charms, psychic abilities and miraculous feats of strength). He usually chickens out when he witnesses said phenomena and implores 奈緒子 to help him explain what's happening.

\par 奈緒子 is insulted by many of the characters due to her small breasts. She usually fights back with a jibe about 上田's gigantic penis, or the fact that the wig that \ruby{矢}{や}\ruby{部}{べ}\ruby{謙}{けん}\ruby{三}{ぞ}\endnote{Yabe Kenzo} wears is has fallen off or looks obvious or out of place.

\par 矢部謙三 is an inept Assistant Detective, sent from Tokyo to investigate the crimes that are related to the phenomena that 上田 and 奈緒子 are trying to debunk. 矢部 (also the Japanese word for ``stop'') is played by \ruby{生}{なま}\ruby{瀬}{せ}\ruby{勝}{かつ}\ruby{久}{ひせ}\endnote{Namase Katsuhise}.

\par 奈緒子's Mother, 山田さとり\endnote{Yamada Satori} is a calligrapher who teaches the children of her home town about the power of the written word. She has an often hinted at but never explained, psychic connection with 奈緒子, and will often find a way of helping her daughter when she is in trouble. She is played by \ruby{野}{の}\ruby{際}{ぎわ}\ruby{陽}{よ}\ruby{子}{こ}\endnote{Nogiwa Yoko}.

\par More information about Trick can be found at the D-Additcs wiki page: \url{http://wiki.d-addicts.com/Trick}

\theendnotes